---
title: "Survival Analysis for Telecommunication Services Subscribers"
author: "University of Miami | Mingjun Li"
date: "2/22/2020"
output: pdf_document
---

A telecommunications company is concerned about the number of customers leaving their landline business for cable competitors. Our goal is to help them understand who is leaving and ultimately propose a retention plan to decrease churn and improve revenues. 
```{r}
library(tidyr)
library(dplyr)
library(pscl)
library(survival)

#install.packages('survminer')
library(survminer)

#install.packages('rlist')
library(rlist)

library(ggpubr)
library(magrittr)
```

```{r}
churn <- read.csv('https://s3.amazonaws.com/douglas2/MAS646/telcoChurn.csv')%>%
  mutate(
    SeniorCitizen = factor(SeniorCitizen,levels=c(1,0)),
    Churn = as.integer((Churn=='Yes')*1)
  )
```
```{r}
names(churn)
```


# Which kind of customer is the most easy to leave?

##(use customer-based info: gender, age range, and if they have partners and dependents)

##Draw KM curve by each group
```{r}
#Survminer includes a function surv_fit that acts as a wrapper around survfit. If you use surv_fit instead of survfit, the "call" of the returned object will include the whole data frame instead of just data = x. surv_fit works better when calling ggsurvplot inside a formula
KMcurve <- function(d,nameVector,time,churn){
  len=length(nameVector)
  sub=d[nameVector]
  # test if there is difference between groups
  dif = lapply(sub, function(q) survdiff(Surv(tenure,Churn)~q,data=d))
  s<-mapply(
            function(group,colname) {
              ggsurvplot(
                         surv_fit(Surv(d$tenure,d$Churn)~group,data=d),
                          data=d,legend.title = colname,font.x=10,font.y=10
                               )}, 
            group = sub, colname = names(sub)
              )
  plot_list=list()
  for (i in 1:len){
    plot_list = list.append(plot_list,s[,i]$plot)
  }
  
  return (list(ggarrange(plotlist=plot_list,ncol=1,nrow=2),dif)) #R function must return a list if multiple return
}
```

##Gender doesnt make any difference

##Senior Citizen, No partner and No dependents are more likely to leave
```{r}
cInfo = names(churn)[2:5]
KMcurve(churn,cInfo,'tenure','Churn')
```

##Phone service is not a determinant of leaving, all the other services have influnce.

##Specifically, customers who doesn't sign up for internet service are most unlikely to stay.

##For internet service, customers who use Fib will more likely to leave than using DSL

##For all the other service, not using service will more likely to leave

## 
```{r}
service = names(churn)[7:15]
KMcurve(churn,service,'tenure','Churn')
```

##Sining for shorter contract will more likely to leave, monthly contract loses times than yearly contract.

## No paperless billing is more likely to leave

## Electronic check is more likely to leave compared with credit card, bank transfer and mailed check
```{r}
unique(churn$PaymentMethod)
```

```{r}
#notice that charge is continuous variable
account = names(churn)[16:18]
KMcurve(churn,account,'tenure','Churn')
```
## In conclusion, our target customers are younger people with partners and dependents.

## In order to retain customer, the overall strategy is to attract more signing up our services. Also, a save and convenient paying environment by credit card and bank transfer will help to retain customers.

```{r}
head(churn)
```
# Revenue
## tenure is month unit

## How much we earn from those without internet service
```{r}
inter <- tapply(churn$MonthlyCharges , churn$InternetService, mean)
inter
```
```{r}
km = survfit(Surv(tenure,Churn) ~ InternetService, data=churn)
print(km, print.rmean = T, rmean=60)
```
```{r}
c(10.9,10.4,11.4)*inter
c(21.1,19.3,22.6)*inter
c(49.9,41.3,55.6)*inter
```



## Monthly charge more and yearly charge less
```{r}
meanCharge = tapply(churn$MonthlyCharges , churn$Contract,mean)
meanCharge
```
## retention rate in specific time range
```{r}
km = survfit(Surv(tenure,Churn) ~ Contract, data=churn)
print(km, print.rmean = T, rmean=30)
```





